### 2024-01-01 chapters/main-contributions.tex
Make some minor updates
Fix decision-support -> decision support
Polish contributions and research hypotheses

The chapters of \cref{part:unsupervised-uncertainty-estimation,part:unsupervised-speech-representation-learning,part:medical-applications} are self-contained studies and therefore detail their own research hypotheses and contributions.
Since each study was written without consideration to the other chapters of the thesis, we here detail them in relation to the overall research project. 
This constitutes the research hypotheses and contributions of the thesis.

@@

\contribitem{part:unsupervised-speech-representation-learning}
This part deals with unsupervised learning of speech representations and consists of two papers. 
The contributions of this part lie in analyzing and comparing different approaches to speech representation along with a comprehensive overview of the field.

\contribitem{chp:paper-brief}
In this chapter, we present a comprehensive overview of unsupervised neural representation learning for speech. Previous research is categorized into self"-supervised methods and probabilistic latent variable models and described in a common notation. This description assists in developing a model taxonomy that shapes a discussion of the models' representational power, the associated learning strategies, and the methods used to evaluate them. The discussion points to interesting avenues of future research. 
An extended version of this overview paper that focuses exclusively on self"=supervised methods was also published as part of the project \ref{enumerate: paper-review} \parencite{mohamed_selfsupervised_2022}. This paper is included in \cref{app:paper-review} for reference.

@@

\contribitem{part:medical-applications}
This part contains two studies on machine learning methods applied for tasks in a medical setting. The contributions of the first are methodological focusing on improved comparability and reproducibility of studies on automated medical coding. The second is a retrospective study on machine learning-assisted stroke recognition focusing on the potential clinical impact of using machine learning to recognize stroke cases in emergency calls. 
While uncertainty estimation is not a central theme to the two papers, the retrospective study performs a substantial evaluation of the explainability of the proposed model via an occlusion analysis on the text input. 
Later, in the discussion, we shall further consider uncertainty estimation in relation to medical applications focusing on the retrospective study.
% \moretodo[inline]{Revise and add more details to this section. Do we discuss uncertainty for medical coding?}

\contribitem{chp:paper-automated}
In this paper, we review the current state-of-the-art in automated medical coding of clinical notes. 
We hypothesize that several previous works underperform for reasons more related to suboptimal hyperparameter tuning, incorrect evaluation, and crude data handling than to model design, and that performance and comparability can be improved by addressing these issues. 
We first reproduce, analyze and compare several models on the MIMIC-III dataset showing that poor performance is indeed attributable to weak configuration of the training and crudely sampled train-test splits with many extremely rare classes - several without examples in the training data. 
We also identify and correct a widespread error in the calculation of the macro F1-score. 
To compare models, we propose new data splits created with stratified sampling, use identical experimental setups and tune hyperparameters and decision boundaries. 
By analyzing prediction errors, we confirm the observation of previous work that all models struggle with rare codes, although, contrary to previous claims, long documents only have a negligible impact on performance. 
Finally, we present the first comprehensive results on the recently released MIMIC-IV dataset using the reproduced models.

>>>>

The chapters of \cref{part:unsupervised-uncertainty-estimation,part:unsupervised-speech-representation-learning,part:medical-applications} are self-contained studies and therefore detail their own research hypotheses and contributions.
Since each study was written without consideration to the other chapters of this thesis, we here detail them in relation to the overall research project. 
This constitutes the research hypotheses and the contributions of the thesis.

@@

\contribitem{part:unsupervised-speech-representation-learning}
This part deals with unsupervised learning of speech representations and consists of two papers. Speech representations are fundamental to any practical system for decision support as well as for uncertainty quantification on speech data. 
The contributions of this part lie in analyzing and comparing different approaches to speech representation and in providing a comprehensive overview of the field.

\contribitem{chp:paper-brief}
In this chapter, we present a comprehensive overview of unsupervised neural representation learning for speech. Previous research is categorized into self"=supervised methods and probabilistic latent variable models and described in a common notation. This description assists in developing a model taxonomy that shapes a discussion of the models' representational power, the associated learning strategies, and the methods used to evaluate them. The discussion points to interesting avenues of future research. 
An extended version of this overview paper that focuses exclusively on self"=supervised methods was also published as part of the project \ref{enumerate: paper-review} \parencite{mohamed_selfsupervised_2022} and this paper is included in \cref{app:paper-review} for reference.

@@

\contribitem{part:medical-applications}
This part contains two studies on machine learning methods applied for tasks in a medical setting. The contributions of the first are methodological focusing on improved comparability and reproducibility of studies on automated medical coding. The second is a retrospective study on machine learning-assisted stroke recognition focusing on the potential clinical impact of using machine learning to recognize stroke cases in emergency calls. 
While uncertainty estimation is not a central theme to the two papers, the retrospective study performs a substantial evaluation of the explainability of the proposed model via an occlusion analysis on the text input. 
Later, in the discussion, we further consider uncertainty estimation in relation to medical applications focusing on the retrospective study (\cref{sec: discussion-stroke-recognition-uncertainty}).
% \moretodo[inline]{Revise and add more details to this section. Do we discuss uncertainty for medical coding?}

\contribitem{chp:paper-automated}
In this paper, we review the current state-of-the-art in automated medical coding of clinical notes. 
We hypothesize that several previous works underperform for reasons more related to suboptimal hyperparameter tuning, incorrect evaluation, and crude data handling than to model design, and that performance and comparability can be improved by addressing these issues. 
We first reproduce, analyze and compare several models on the MIMIC-III dataset showing that poor performance is indeed attributable to weak configuration of the training and poorly sampled train-test splits with many extremely rare classes - several without examples in the training data. 
We also identify and correct a widespread error in the calculation of the macro F1-score. 
To compare models, we propose new data splits created with stratified sampling, use identical experimental setups and tune hyperparameters and decision boundaries. 
By analyzing prediction errors, we confirm the observation of previous work that all models struggle with rare codes, although, contrary to previous claims, long documents only have a negligible impact on performance. 
Finally, we present the first comprehensive results on the recently released MIMIC-IV dataset using the reproduced models.
